\begin{acknowledge} 
My time at graduate school has been a long road that has been greatly enriched
by my many fantastic colleagues and mentors. I would like to especially thank
my advisor, Professor J. Daniel Gezelter, for his guidance and support
throughout this research. His piercing insights, expertise in coding, and
skills as an educator have helped me grow as a researcher and a teacher. I am
indebted to my former and present group members and colleagues, Dr. Shenyu
Kuang, Dr. James Marr, Dr.  Kelsey Stocker, Dr. Zack Terranova, Dr. Mary
Sherman, Madan Lamichhane, Patrick Louden, Suzanne Neidhart, Patrick McIntyre,
Heather Chiarello, Andrew Latham, and Thomas Parsons for many helpful
discussions, research related or otherwise.

I am extremely grateful to the Kaneb Center and its staff, especially Kristi
Rudenga, as well as my co-graduate student associates, Andre Audette, Amy
Buchmann, Justus Ghormley, Megan Hall, and Kelly Warmuth (Kuznicki) for many
great discussions and workshops filled with teaching and pedagogy. I also owe
many thanks to Dr. Lappin, James Johnson, Sarah West, Steven Weitstock, and Dr.
Gezelter for the experience I gained while assisting them in classes and labs.

I am very thankful to my committee members, Professor J. Daniel Gezelter,
Professor Steven A. Corcelli, and Professor Gregory V. Hartland for their many
helpful questions and suggestions which have help me navigate through this process. 

I must not forgot to mention the administrative assistance and encouragement I
received from Deb Bennet, Cheryl Copley, Amanda Huerta, and the rest of the
Chemistry and Biochemistry Department.

Finally, I would like to acknowledge my best friend and wife, Karen Hooge
Michalka. The love and support she has shown me throughout my time at Notre
Dame, especially while I have been writing and applying for jobs has helped
more than she knows.
\end{acknowledge}

